Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-30 sections/approach.tex

% Our proposed approach is empirically driven and automatically adjusts to the quality the data.
While our proposed approach is straightforward, empirically driven, and automatically adjusts to the quality of the data, it has a few drawbacks.
First, we have to accept that some comments cannot be reliably or confidently classified.
We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.  
% empirically driven and automatically adapts to the quality the data

>>>>

% Our proposed approach is empirically driven and automatically adjusts to the quality the data.
While our proposed approach is straightforward, empirically driven, and automatically adjusts to the quality of the data, it has a few drawbacks.
First, we have to accept that some comments cannot be reliably or confidently classified.
We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.

% empirically driven and automatically adapts to the quality the data

### 2014-07-30 sections/results.tex

\begin{table*}[!t]
\caption{Results from bootstrapping cross validation of our classification models against random models}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{cccc|cc|cc}
\hline
\multicolumn{2}{c}{Classifcation}   & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c}{F-measure} \\ \cline{3-8}
\multicolumn{2}{c}{Models} & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
\multirow{2}{*}{Useful} & $\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089\\ \cline{2-8}
& Random     &  0.421 & 0.114 &  0.376 & 0.116 & 0.496 & 0.144\\ \hline
\multirow{2}{*}{Useless}  & $\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118\\ \cline{2-8}
& Random    &  0.336 & 0.131 &  0.269 & 0.115 & 0.478 & 0.182\\
\hline
\end{tabular}
\label{tb:xvalidate}
\end{table*}

@@

On average, it takes 28 seconds to assess each comment.
However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess; only few comments take long time.
This also suggests that the time to assess each comment is not normally distributed.
The standard deviation is 45 seconds.

@@

However, to manually assess all 10,583 comments---even with only one person working at 10 comments per minute---this would take 17.6 person hours.
By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
That means that about 77\% of the effort is saved.

>>>>

\begin{table*}[!t]
\caption{Results from bootstrapping cross validation of our classification models against random models}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{cccc|cc|cc|cc}
\hline
\multicolumn{2}{c}{Classifcation}   & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c|}{F-measure} & \multicolumn{2}{c}{Accuracy} \\ \cline{3-10}
\multicolumn{2}{c}{Models} & Avg. & STD. & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
\multirow{2}{*}{Useful} & $\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089 & 0.752 & 0.067 \\ \cline{2-10}
& Random     &  0.421 & 0.114 &  0.376 & 0.116 & 0.496 & 0.144 & 0.496 & 0.089 \\ \hline
\multirow{2}{*}{Useless}  & $\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118 & 0.815 & 0.064 \\ \cline{2-10}
& Random    &  0.336 & 0.131 &  0.269 & 0.115 & 0.478 & 0.182 & 0.500 & 0.089 \\
\hline
\end{tabular}
\label{tb:xvalidate}
\end{table*}

@@

On average, it takes 28 seconds to assess each comment.
However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
This also suggests that the time to assess each comment is not normally distributed.
The standard deviation is 45 seconds.

@@

However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
That means that about 77\% of the effort is saved.

Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the figure shows, the proportion is similar to the result of .

\begin{table}[!t]
\caption{Proportion of classifications when applied to the whole data set.}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Class &        over all samples & only training data  \\ \hline
useful &            42.8\%      &      41.8\%         \\
useless &           33.7\%      &      33.1\%         \\
undetermined &      23.5\%      &      25.1\%         \\ \hline
\end{tabular}
\label{tb:percent}
\end{table}

%\pick{Note from Dan sensei,}
%For cpost effectivness we can state the reduction  percentage in the number of comments that much be checked manually.
% Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!
%You cannot, but some estimates are possble
%first, human beings have a fairly well known rate of making errors in classification
%second, look at the comments in the training set that the method classified differently, especially the unclear.
%Review these to see if the method suggested a better classification than was originally made by the assessors
%You can consider these errors. Now look at what wans the percent of errors in the training set
%This is also an estimate of the human error rate
